### 2020-06-03 discussion.tex
Added text about monitoring improvements.

>>>>

\rev{The experienced reliability issues with Titan had a direct impact on the
development and deployment of Titan's successor, Summit, and even on Summit's
successor, Frontier. As a result, more and better monitoring data is already
collected on Summit. NVIDIA's GPU management and monitoring software has been
significantly improved. Temperature monitoring has been significantly improved
as well.}
